Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
experiment with canging the codebook size updated
remove merge problem

% NEW RESULTS COMING SOON WITH FIXED SIZED DATASET
\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.066079$ \\
10 & $5$K & $0.045690$ \\
50 & $25$K & $0.038456$ \\
100 & $50$K & $0.036725$ \\
200 & $100$K & $0.033923$ \\
500 & $250$K & $0.030973$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{\small{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. The number of training
samples is set to $500$ times the number of codes. 
NEW RESULTS COMING SOON WITH FIXED SIZED DATASET }}
\label{tab:cbsize}
\end{table}

@@

>>>>>>>>>>>>>>>>>>>> File 1
>>>>>>>>>>>>>>>>>>>> File 2
Crazy idea: chord recognition via quantization: transcribe codewords,
then just encode song to get chords. would this work?
>>>>>>>>>>>>>>>>>>>> File 3
<<<<<<<<<<<<<<<<<<<<

>>>>

% NEW RESULTS COMING SOON WITH FIXED SIZED DATASET
\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & distortion \\ \hline \hline
1 & $0.066081$ \\
10 & $0.045579$ \\
50 & $0.038302$ \\
100 & $0.035904$ \\
500 & $0.030841$ \\ \hline
\end{tabular}
\end{center}
\caption{\small{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. 
The number of training samples is $50000$.
}}
\label{tab:cbsize}
\end{table}

@@
